The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2009-08-10 script/de/chapters/numbertheory.tex
CT script, Appendixes in chap 2, 3 and 4 named in the same way (de+en)

$1000100101110101 = 1001$ (mod $1010)  \Longrightarrow a_0 = 9$, ~ ~ $1000100101110101 / 1010 = 110110111110$ \\
$110110111110 = 1000$ (mod $1010) \Longrightarrow a_1 = 8$, $110110111110 / 1010 = 101011111$ \\
$101011111 = 1$ (mod $1010) \Longrightarrow a_2 = 1$, $10101111 / 1010 = 100011$ \\
$100011 =  101$ (mod $1010) \Longrightarrow a_3 = 5$, $100011 / 1010 = 1$ \\
$11 = 11$ (mod $1010) \Longrightarrow a_4 = 3$ \\
Damit ergibt sich $z = 35189$. 
\end{example}
% End of Base representation and base transformation of numbers.

>>>>

\noindent $1000100101110101 = 1001$ (mod $1010)  \Longrightarrow a_0 = 9$, ~ ~ $1000100101110101 / 1010 = 110110111110$ \\
$110110111110 = 1000$ (mod $1010) \Longrightarrow a_1 = 8$, $110110111110 / 1010 = 101011111$ \\
$101011111 = 1$ (mod $1010) \Longrightarrow a_2 = 1$, $10101111 / 1010 = 100011$ \\
$100011 =  101$ (mod $1010) \Longrightarrow a_3 = 5$, $100011 / 1010 = 1$ \\
$11 = 11$ (mod $1010) \Longrightarrow a_4 = 3$ \\
Damit ergibt sich $z = 35189$. 
\end{example}
% End of Base representation and base transformation of numbers.

### 2009-08-10 script/de/chapters/primes.tex
CT script, Appendixes in chap 2, 3 and 4 named in the same way (de+en)

% --------------------------------------------------------------------------
\newpage
\hypertarget{primhfk}{}
\subsection{Anzahl von Primzahlen in verschiedenen Intervallen}
\label{s:primhfk}
\vskip +10 pt

@@

% --------------------------------------------------------------------------
\newpage
\hypertarget{ntePrimzahl}{}
\subsection{Indizierung von Primzahlen ($n$-te Primzahl)}
\label{s:ntePrimzahl}
\vskip +10 pt

@@

% --------------------------------------------------------------------------
\newpage
\subsection{Größenordnungen / Dimensionen in der Realität}
\label{s:grosord}
Bei der Beschreibung kryptographischer Protokolle und Algorithmen
treten Zahlen auf, die so groß bzw. so klein sind, dass sie einem
intuitiven Verständnis nicht zugänglich sind. Es kann daher
nützlich sein, Vergleichszahlen aus der uns umgebenden realen
Welt bereitzustellen, so dass man ein Gefühl für die Sicherheit
kryptographischer Algorithmen entwickeln kann. Die angegebenen
Werte stammen größtenteils aus \cite{pr:Schwenk1996} und
\cite[S.18]{pr:Schneier1996p}.  \hypertarget{grosord}{}

@@

% --------------------------------------------------------------------------
\newpage
\subsection{Spezielle Werte des Zweier- und Zehnersystems}

@@

% ---------------------------------------------------------------------------
% ---------------------------------------------------------------------------
\newpage
\hypertarget{Primes_Appendix_A}{}
\section{Beispiele mit Sage}
% \section*{Appendix A: Beispiele mit Sage}
% \addcontentsline{toc}{section}{Appendix A: Beispiele mit Sage}
\label{Primes_Sage_samples}
\index{Sage!Programmbeispiele}
\index{Sage}

>>>>

% --------------------------------------------------------------------------
\newpage
\hypertarget{primhfk}{}
\section{Anhang: Anzahl von Primzahlen in verschiedenen Intervallen}
\label{s:primhfk}
\vskip +10 pt

@@

% --------------------------------------------------------------------------
\newpage
\hypertarget{ntePrimzahl}{}
\section{Anhang: Indizierung von Primzahlen ($n$-te Primzahl)}
\label{s:ntePrimzahl}
\vskip +10 pt

@@

% --------------------------------------------------------------------------
\newpage
\section{Anhang: Größenordnungen / Dimensionen in der Realität}
\label{s:grosord}
Bei der Beschreibung kryptographischer Protokolle und Algorithmen
treten Zahlen auf, die so groß bzw. so klein sind, dass sie einem
intuitiven Verständnis nicht zugänglich sind. Es kann daher
nützlich sein, Vergleichszahlen aus der uns umgebenden realen
Welt bereitzustellen, so dass man ein Gefühl für die Sicherheit
kryptographischer Algorithmen entwickeln kann. Die angegebenen
Werte stammen größtenteils aus \cite{pr:Schwenk1996} und
\cite[S.18]{pr:Schneier1996p}.  \hypertarget{grosord}{}

@@

% --------------------------------------------------------------------------
\newpage
\section{Anhang: Spezielle Werte des Zweier- und Zehnersystems}

@@

% ---------------------------------------------------------------------------
% ---------------------------------------------------------------------------
\newpage
\hypertarget{Primes_Appendix_A}{}
\section{Anhang: Beispiele mit Sage}
% \section*{Appendix A: Beispiele mit Sage}
% \addcontentsline{toc}{section}{Appendix A: Beispiele mit Sage}
\label{Primes_Sage_samples}
\index{Sage!Programmbeispiele}
\index{Sage}

### 2009-08-10 script/en/chapters/primes.tex
CT script, Appendixes in chap 2, 3 and 4 named in the same way (de+en)

% --------------------------------------------------------------------------
\newpage
\hypertarget{primhfk}{}
\subsection{Number of prime numbers in various intervals}
\label{s:primhfk}
\vskip +10 pt

@@

% --------------------------------------------------------------------------
\newpage
\hypertarget{ntePrimzahl}{}
\subsection{Indexing prime numbers ($n$-th prime number)} 
\label{s:ntePrimzahl}
\vskip +10 pt

@@

% --------------------------------------------------------------------------
\newpage
\subsection{Orders of magnitude / dimensions in reality}
\label{s:grosord}
In the description of cryptographic protocols and algorithms, numbers 
occur that are so large or so small that they are inaccessible to our 
intuitive understanding. It may therefore be useful to provide comparative 
numbers from the real world around us so that we can develop a feeling for 
the security of cryptographic algorithms. Some of the numbers listed below 
originate from \cite{pr:Schwenk1996} and \cite[p.18]{pr:Schneier1996p}.  
\hypertarget{grosord}{}

@@

% --------------------------------------------------------------------------
\newpage
\subsection{Special values of the binary and decimal system}

@@

% ---------------------------------------------------------------------------
% ---------------------------------------------------------------------------
\newpage
\hypertarget{Primes_Appendix_A}{}
\section{Examples using Sage}
% \section*{Appendix A: Examples using Sage}
% \addcontentsline{toc}{section}{Appendix A: Examples using Sage}
\label{Primes_Sage_samples}
\index{Sage!Code examples}
\index{Sage}

>>>>

% --------------------------------------------------------------------------
\newpage
\hypertarget{primhfk}{}
\section{Appendix: Number of prime numbers in various intervals}
\label{s:primhfk}
\vskip +10 pt

@@

% --------------------------------------------------------------------------
\newpage
\hypertarget{ntePrimzahl}{}
\section{Appendix: Indexing prime numbers ($n$-th prime number)} 
\label{s:ntePrimzahl}
\vskip +10 pt

@@

% --------------------------------------------------------------------------
\newpage
\section{Appendix: Orders of magnitude / dimensions in reality}
\label{s:grosord}
In the description of cryptographic protocols and algorithms, numbers 
occur that are so large or so small that they are inaccessible to our 
intuitive understanding. It may therefore be useful to provide comparative 
numbers from the real world around us so that we can develop a feeling for 
the security of cryptographic algorithms. Some of the numbers listed below 
originate from \cite{pr:Schwenk1996} and \cite[p.18]{pr:Schneier1996p}.  
\hypertarget{grosord}{}

@@

% --------------------------------------------------------------------------
\newpage
\section{Appendix: Special values of the binary and decimal system}

@@

% ---------------------------------------------------------------------------
% ---------------------------------------------------------------------------
\newpage
\hypertarget{Primes_Appendix_A}{}
\section{Appendix: Examples using Sage}
% \section*{Appendix A: Examples using Sage}
% \addcontentsline{toc}{section}{Appendix A: Examples using Sage}
\label{Primes_Sage_samples}
\index{Sage!Code examples}
\index{Sage}
